Estimating contemporary migration numbers of adults for iteroparous species based on kinship relationships found between populations

### 2022-02-15 latex/ms.tex
add abstract

\documentclass[12pt, English]{article}
\usepackage{geometry}
\geometry{verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,lmargin=2.54cm,rmargin=2.54cm}
%\usepackage{apacite}
\usepackage[natbibapa]{apacite}
%\renewcommand{\APACrefYearMonthDay}[3]{\APACrefYear{#1} 
%  \cite<pre>[post]{key}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{boxedminipage}
\usepackage{oldgerm}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{wrapfig}
\usepackage{indentfirst}
\usepackage{mathptmx}
\usepackage{setspace}
\usepackage{lscape} 
\usepackage[mathlines]{lineno}
\renewcommand{\ttdefault}{mathptmx}
\usepackage[latin9]{inputenc}
\usepackage{bm}
\usepackage{relsize}
\usepackage[normalem]{ulem} %%
\linenumbers
\usepackage{bm}
\setlength{\parindent}{20pt}
\usepackage[labelformat=empty,labelsep=none]{caption}
\usepackage[singlelinecheck=false]{caption}
\usepackage{color}
\def\RED#1{\textcolor{red}{#1}} %% 
\def\BLUE#1{\textcolor{blue}{#1}} %% 
\begin{document}

\title{Estimating contemporary migration numbers of adults for iteroparous species using kinship pairs found between populations}
\author{
Tetsuya Akita$^{a}$\thanks{
\emph{Corresponding author}:
    Fisheries Resources Institute, Fisheries Research and Education Agency, Kanagawa 236-8648, Japan.
    E-mail: akitatetsuya1981@affrc.go.jp} \\ 
   \small $^{a}$Fisheries Resources Institute, Fisheries Research and Education Agency, \\
   \small Kanagawa, 236-8648, Japan.
   }
\date{Manuscript Intended for \emph{Methods in Ecology and Evolution}, \today}
\maketitle

\begin{abstract}
本ノートでは，多回繁殖(iteroparity)する種を対象として，半兄弟ペア数から親魚による２つのサブ集団間の移動率を推定する理論($\hat{M}=N_1N_2H_{\rm obs}/(4n_1n_2)$)を紹介する。この推定式は、親をサンプルする通常の標識放流と同じである。もし、繁殖ポテンシャルの分布が集団間で異なっていても上記の式で問題ないことを示した。一方，サンプル数としては$\sqrt {N}$以上のオーダーが求められる。
\\
\end{abstract}
\textbf{Key words:} effective population size; sibship assignment; overdispersed reproduction; close-kin mark-recapture\\
\textbf{Running head:} Estimating migration rates using kinship pairs\\

@@

Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the known kinship information in a sample \cite[reviewed in][]{https://doi.org/10.1111/faf.12615}. The rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in the MR method. Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect an adult number in the population \cite[]{bravington2016close}. While recent studies of CKMR argued that availability of kinship information in estimating the migration rate \cite[]{https://doi.org/10.1002/ece3.6296, 10.1093/icesjms/fsac002}, the CKMR-based migration estimation has not been well developed and rigorously examined in a simulation study.

@@

In this study, we propose a new method for estimating the contemporary migration number or rate of adults between two pre-defined populations in iteroparous species, where the migration direction is specified. Assuming that kinships are genetically detected without any error, this method is based on the numbers of half-sibling (HS) and parent-offspring (PO) pairs in a sample. Sampling can be invasive or non-invasive and is completed at two breeding seasons; sampling offspring (young-of-year individuals) and parents probably shares PO relationship with sampled offspring in the one population at the first breeding season and in the another population at the second breeding season. The rationale is that the number of PO and HS pairs found between populations have information as to how often parental movements during the breeding interval are realized. Our model explicitly incorporates reproductive variation within and between populations, making it possible to target a species whose fertility is affected by environmental differences between populations. First, we explain the modeling assumption and sampling scheme. Then, we analytically determine the estimators of the contemporary migration number or rate of adults, which are based on the numbers of HS and/or PO pairs. Finally, by running an individual-based model, we investigate the performance of the estimator and provide a guide for a sample size. It is noteworthy that our modeling framework can be applied to diverse animal species. However, the description of the model focuses on fish species, which are presently the best candidate target of our proposed method.

\section{Theory}\label{sec2}
In this section, we present the theoretical foundation for estimating a migrant number and a migration rate of iteroparous species using HS or PO pairs, which are found between two populations with a different sample timing. While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix 2}), here we assume a relatively simple situation for explanation purposes. The main symbols used in the current paper are summarized in {\bf Table \ref{symbols}}.

@@

Suppose that we have a set of two populations labelled 1 and 2 where random mating occurs within each population and that parents can move to the other population after the end of the reproductive season. Hereafter, without loss of generality, we consider the movement of parents in the direction from population 1 to population 2 and focus on the migration number or rate, and that is what we attempt to estimate. In this framework, we show that considering two reproductive seasons (hereafter, we call them "the first year" and "the second year") is enough to estimate it. {\bf Figure \ref{cartoon}a} presents a schematic representation of the kinship relationships and movements of parents.

@@

Next, we consider the probability that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship, denoted by $\pi_{\rm PO, bet}$. $\pi_{\rm PO, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a migrant; (ii) the probability that a migrant is sampled; and (iii) the probability that the migrant of a sampled offspring in the population 1 and the migrant sampled in the population 2 are identical. The first and second probabilities are the same as the one introduced in the previous subsection, that is, $2M/N_{1}$ and $1/M$. The second probability is $M/N_{2}$ by definition. Taken together, we obtain
\begin{align}
\pi_{\rm PO,bet} &= \frac{2M}{N_{1}} \frac{M}{N_{2}} \frac{1}{M} \nonumber\\
&= \frac{2M}{N_{1}N_{2}}.
\label{PO-1}
\end{align}
This form also holds under a flexible setting for the reproductive potential, as noted in {\bf Appendix}. If all $N_1$ parents safely move to the population 2 (i.e., $M = N_1$), $\pi_{\rm PO,bet}$ equals $2/N_2$; meanwhile, if the population 2 consists only of migrants (i.e., $M = N_2$), $\pi_{\rm PO,bet}$ equals $2/N_1$. These probabilities in the extreme cases are similar forms to PO probability that is randomly sampled within a population \cite[]{bravington2016close}.

@@

Proposed estimators are based on the observed number of kinship pairs. Their expected number is linearly determined by the number of pairwise comparison (Eqs.~\ref{HS-2-1}-\ref{HS-2-2} and \ref{PO-2-1}-\ref{PO-2-2}), providing guidance for a sample size to ensure the condition that at least one or more kinship pairs can be found. The conditions are given by
\begin{align}
n_{\rm O, 1} n_{\rm O, 2} &> \frac{ N_{2} } { 4m },
\label{RS-1}
\end{align}
and
\begin{align}
n_{\rm O, 1} n_{\rm P, 2} &> \frac{ N_{2} } { 2m }.
\label{RS-2}
\end{align}
Roughly speaking, required sample size to ensure above conditions is that $n>\sqrt{N_2}$, where $n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$. It should be noted that very tiny $m$, which dramatically increases the required sample size, produces significant genetic differences between two populations. In such a case, there are several methods to estimate migration rate by population genetics technique; alternatively, we focus the situation of moderate/large migration rate, which leads little genetic differences between two populations (see details in {\bf Discussion} section).

@@

We numerically evaluated the performance of ${\hat M}$s or ${\hat m}$s for the case in which variable reproductive potential among parents. Scaled statistical properties of ${\hat m_1}$,  ${\hat m_2}$,  ${\hat m_3}$ and ${\hat m_4}$ are completely the same to ${\hat M_1}$, ${\hat M_2}$, ${\hat M_3}$ and ${\hat M_4}$, hereafter, we only demonstrate the results of ${\hat M_1}$-${\hat M_5}$. {\bf Figure~\ref{violins}} illustrates the distribution of the relative bias of ${\hat M}$ for limiting cases where parent and offspring sample numbers are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$) and parent numbers in the two populations are also identical (i.e., $N=N_1=N_2$). Relative bias is calculated by applying outputs of the individual-based model, which is defined as follows: ``averaged estimator - true value/true value.'' Full list of parameter sets to evaluate the performance (relative bias and CV of ${\hat M}$s) is summarized in {\bf Table S1} in {\bf Supporting Information}.

@@

Our simulator can handle the situation with or without invasive sampling. Invasive sampling potentially affects the degree of $m$ since sampled parents in the population 1 have no chance to move to the population 2 and thus those parents cannot be sampled. In this case, $m$ should be defined by $M/(N_1-n_{P,1})$ not by $M/N_1$, although it does not affect the estimator ${\hat M}$s, as demonstrated in {\bf Table S1} ({\bf Supporting Information}).

Finally, we investigated the situation in which the parental number in the population 1 is much more than in the population 2 (i.e., $N_1 \gg N_2$) and thus migrants are large proportion of $N_2$. In such a setting, e.g., $(N_1,N_2,M)=(10^4,10^3,500)$, we confirmed the same property of ${\hat M}$s to the situation $N_1 = N_2$, as demonstrated in {\bf Table S1} ({\bf Supporting Information}), suggesting the robustness of ${\hat M}$s in heterogeneous population sizes.

@@

\renewcommand{\theequation}{A\arabic{equation}}
Here, we introduce the concept of the reproductive potential of parent $i$ and $j$ in the population 1 and 2, respectively, which are defined as the expected number of surviving offspring at sampling time, denoted by $\lambda_{i,1}$ and $\lambda_{j,2}$ ($i=(1, \ldots, N_1)$ and $j=(1, \ldots, N_2)$). The reproductive potential is determined by several factors, including the parent's age, weight, residence time on the spawning ground. It should be noted that the magnitude of this parameter includes information about the survival rate of the offspring, the number of days after egg hatching, and the egg number; this implies that the parameter reflects the sample timing. It should also be noted that the modeling framework does not depend on whether the reproductive potential is heritable or not.

@@

In the process of the derivation of $\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$ in {\bf APPENDIX 2}, we ignore covariation between migration and reproductive potential. Here, we consider the situation in which migrants have a distinguishable distribution of reproductive potential from non-migrant parents. Let $\lambda_{i,1}$, $\lambda_{j,2}$, $\lambda_{M,l,1}$ and $\lambda_{M,l,2}$ be a reproductive potential of non-migrant in the population 1 and 2 and migrants in the population 1 and 2 with mean ${\bar \lambda_{1}}$, ${\bar \lambda_{2}}$, ${\bar \lambda_{M,1}}$ and ${\bar \lambda_{M,2}}$, respectively. Under this setting, $\pi_{\rm HS,bet}$ can be written by
\begin{align}
\pi_{\rm HS,bet} &\approx \frac{4}{M}  \frac{ \mathbb{E}\left[ \sum_{l=1}^M \lambda_{M,l,1} \sum_{l=1}^M \lambda_{M,l,2} \right]} {\mathbb{E}\left[ \left(\sum_{l=1}^{M} \lambda_{M,l,1} + \sum_{i=M+1}^{N_1} \lambda_{i,1}\right) \left(\sum_{l=1}^{M} \lambda_{M,l,2} + \sum_{j=M+1}^{N_2} \lambda_{j,2}\right) \right] }\nonumber\\ 
&= \frac{4}{M} \frac{ M^2 {\bar \lambda_{M,1}} {\bar \lambda_{M,2}} } { M {\bar \lambda_{M,1}} + (N_1 - M) {\bar \lambda_1} + M {\bar \lambda_{M,2}} + (N_2 - M) {\bar \lambda_2} }.
\label{App3}
\end{align}
If ${\bar \lambda_{M,1}} = {\bar \lambda_{1}}$ and ${\bar \lambda_{M,2}} = {\bar \lambda_{2}}$, Eq.~\ref{App3} reduces to Eq.\ref{App2}. This formulation include reproductive potential terms, so that distinct reproductive potential between migrants and non-migrants vanishes the usefulness from proposed HS-based estimators (this is also applied to PO-based estimators proposed in this paper).

>>>>

\documentclass[12pt, English]{article}
\usepackage{geometry}
\geometry{verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,lmargin=2.54cm,rmargin=2.54cm}
%\usepackage{apacite}
\usepackage[natbibapa]{apacite}
%\renewcommand{\APACrefYearMonthDay}[3]{\APACrefYear{#1} 
%  \cite<pre>[post]{key}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{boxedminipage}
\usepackage{oldgerm}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{wrapfig}
\usepackage{indentfirst}
\usepackage{mathptmx}
\usepackage{setspace}
\usepackage{lscape} 
\usepackage[mathlines]{lineno}
\renewcommand{\ttdefault}{mathptmx}
\usepackage[latin9]{inputenc}
\usepackage{bm}
\usepackage{relsize}
\usepackage[normalem]{ulem} %%
\linenumbers
\usepackage{bm}
\setlength{\parindent}{20pt}
\usepackage[labelformat=empty,labelsep=none]{caption}
\usepackage[singlelinecheck=false]{caption}
\usepackage{color}
\def\RED#1{\textcolor{red}{#1}} %% 
\def\BLUE#1{\textcolor{blue}{#1}} %%

% https://onlinelibrary.wiley.com/page/journal/17550998/homepage/forauthors.html

\begin{document}

\title{Estimating contemporary migration numbers of adults for iteroparous species based on kinship relationships found between populations}
\author{
Tetsuya Akita$^{a}$\thanks{
\emph{Corresponding author}:
    Fisheries Resources Institute, Fisheries Research and Education Agency, Kanagawa 236-8648, Japan.
    E-mail: akitatetsuya1981@affrc.go.jp} \\ 
   \small $^{a}$Fisheries Resources Institute, Fisheries Research and Education Agency, \\
   \small Kanagawa, 236-8648, Japan.
   }
\date{Manuscript Intended for \emph{Molecular Ecology and Resources}, \today}
\maketitle

\begin{abstract}
This study develops estimators of the contemporary migration number and rate of adults for iteroparous species between two populations. The proposed estimators are based on both known half-sibling (HS) and/or parent-offspring (PO) relationships observed between the populations across the breeding seasons. The rationale is that such HS and PO pairs have information as to how often parental movements during the breeding interval are realized. Our method allows for variance of the average number of offspring per parent within and between populations. In addition, coupled with PO pairs found within population, the estimators can be obtained only from genetic data. Roughly speaking, a sample size of square root of population size is required for obtaining meaningful information on migration. We also evaluate the detailed performance of the estimators by running an individual-based model, providing a guidance for sample sizes to ensure the required accuracy and precision. Furthermore, in the face of the current situation where there is little effective method for estimating adult movement especially when populations cannot be genetically distinct, we discuss the usefulness of this proposed sibship assignment method in terms of conservation biology and wildlife management.  
\\
\end{abstract}

\textbf{Key words:} dispersion; sibship assignment; reproductive potential; close-kin mark-recapture\\
\textbf{Running head:} Estimating migration numbers using kinship pairs\\
\textbf{Subject Area:} Molecular and Statistical Advances\\

@@

Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the known kinship information in a sample \cite[][and references therein]{https://doi.org/10.1111/faf.12615}. The rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in the MR method. Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect an adult number in the population \cite[]{bravington2016close}. While recent studies of CKMR argued that availability of kinship information in estimating the migration rate \cite[]{https://doi.org/10.1002/ece3.6296, 10.1093/icesjms/fsac002}, the CKMR-based migration estimation has not been well developed and rigorously examined in a simulation study.

@@

In this study, we propose a new method for estimating the contemporary migration number or rate of adults between two pre-defined populations in iteroparous species, where the migration direction is specified. Assuming that kinships are genetically detected without any error, this method is based on the numbers of half-sibling (HS) and parent-offspring (PO) pairs in a sample. Sampling can be invasive or non-invasive and is completed at two breeding seasons; sampling offspring (young-of-year individuals) and parents probably shares PO relationship with sampled offspring in the one population at the first breeding season and in the another population at the second breeding season. The rationale is that the number of HS and PO pairs found between populations have information as to how often parental movements during the breeding interval are realized. Our model explicitly incorporates reproductive variation within and between populations, making it possible to target a species whose fertility is affected by environmental differences between populations. First, we explain the modeling assumption and sampling scheme. Then, we analytically determine the estimators of the contemporary migration number or rate of adults, which are based on the numbers of HS and/or PO pairs. Finally, by running an individual-based model, we investigate the performance of the estimator and provide a guide for a sample size. It is noteworthy that our modeling framework can be applied to diverse animal species. However, the description of the model focuses on fish species, which are presently the best candidate target of our proposed method.

\section{Theory}\label{sec2}
In this section, we present the theoretical foundation for estimating a migrant number and migration rate of iteroparous species using HS or PO pairs, which are found between two populations with a different sample timing. While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix 2}), here we assume a relatively simple situation for explanation purposes. The main symbols used in the current paper are summarized in {\bf Table \ref{symbols}}.

@@

Suppose that we have a set of two populations labelled 1 and 2 where random mating occurs within each population and that parents can move to the other population after the end of the reproductive season. Hereafter, without loss of generality, we consider the movement of parents in the direction from the population 1 to the population 2 and focus on the migration number or rate, and that is what we attempt to estimate. In this framework, we show that considering two reproductive seasons (hereafter, we call them "the first year" and "the second year") is enough to estimate it. {\bf Figure \ref{cartoon}a} presents a schematic representation of the kinship relationships and movements of parents.

@@

Next, we consider the probability that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship, denoted by $\pi_{\rm PO, bet}$. $\pi_{\rm PO, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a migrant; (ii) the probability that a migrant is sampled; and (iii) the probability that the migrant of a sampled offspring in the population 1 and the migrant sampled in the population 2 are identical. The first and third probabilities are the same as the one introduced in the previous subsection, that is, $2M/N_{1}$ and $1/M$. The second probability is $M/N_{2}$ by definition. Taken together, we obtain
\begin{align}
\pi_{\rm PO,bet} &= \frac{2M}{N_{1}} \frac{M}{N_{2}} \frac{1}{M} \nonumber\\
&= \frac{2M}{N_{1}N_{2}}.
\label{PO-1}
\end{align}
This form also holds under a flexible setting for the reproductive potential, as noted in {\bf Appendix}. If all $N_1$ parents safely move to the population 2 (i.e., $M = N_1$), $\pi_{\rm PO,bet}$ equals $2/N_2$; meanwhile, if the population 2 consists only of migrants (i.e., $M = N_2$), $\pi_{\rm PO,bet}$ equals $2/N_1$. These probabilities in the extreme cases are similar forms to PO probability that is randomly sampled within a population \cite[]{bravington2016close}.

@@

Proposed estimators are based on the observed number of kinship pairs. Their expected number is linearly determined by the number of pairwise comparison (Eqs.~\ref{HS-2-1}-\ref{HS-2-2} and \ref{PO-2-1}-\ref{PO-2-2}), providing guidance for a sample size to ensure the condition that at least one or more kinship pairs can be found. The conditions are given by
\begin{align}
n_{\rm O, 1} n_{\rm O, 2} &> \frac{ N_{2} } { 4m },
\label{RS-1}
\end{align}
and
\begin{align}
n_{\rm O, 1} n_{\rm P, 2} &> \frac{ N_{2} } { 2m }.
\label{RS-2}
\end{align}
Roughly speaking, required sample size to ensure above conditions is that $n>\sqrt{N_2}$, where $n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$. It should be noted that very tiny $m$, which dramatically increases the required sample size, produces significant genetic differences between two populations. In such a case, there are several methods to estimate migration rate by population genetics technique; alternatively, we focus the situation of moderate/large migration rate, which leads little genetic differences between two populations.

@@

We numerically evaluated the performance of ${\hat M}$s or ${\hat m}$s for the case in which variable reproductive potential among parents. Scaled statistical properties of ${\hat m_1}$,  ${\hat m_2}$,  ${\hat m_3}$ and ${\hat m_4}$ are completely the same to ${\hat M_1}$, ${\hat M_2}$, ${\hat M_3}$ and ${\hat M_4}$, hereafter, we only demonstrate the results of ${\hat M_1}$-${\hat M_5}$. {\bf Figure~\ref{violins}} illustrates the distribution of the relative bias of ${\hat M}$ for limiting cases where parent and offspring sample numbers are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$) and parent numbers in the two populations are also identical (i.e., $N=N_1=N_2$). Relative bias is calculated by applying outputs of the individual-based model, which is defined as follows: ``(averaged estimator - true value)/true value.'' Full list of parameter sets to evaluate the performance (relative bias and CV of ${\hat M}$s) is summarized in {\bf Table S1} in {\bf Supporting Information}.

@@

Our simulator can handle the situation with or without invasive sampling. Invasive sampling potentially affects the level of $m$ since sampled parents in the population 1 have no chance to move to the population 2 and thus those parents cannot be sampled. In this case, $m$ should be defined by $M/(N_1-n_{P,1})$ not by $M/N_1$, although it does not affect the estimator ${\hat M}$s, as demonstrated in {\bf Table S1} ({\bf Supporting Information}).

Finally, we investigated the situation in which the parental number in the population 1 is much more than in the population 2 (i.e., $N_1 \gg N_2$) and thus migrants are large proportion of $N_2$. In such a setting, e.g., $(N_1,N_2,M)=(10^4,10^3,500)$, we confirmed the similar property of ${\hat M}$s to the situation $N_1 = N_2$, as demonstrated in {\bf Table S1} ({\bf Supporting Information}), suggesting the robustness of ${\hat M}$s in heterogeneous population sizes.

@@

\renewcommand{\theequation}{A\arabic{equation}}
Here, we introduce the concept of the reproductive potential of parent $i$ and $j$ in the population 1 and 2, respectively, which are defined as the expected number of surviving offspring at sampling time, denoted by $\lambda_{i,1}$ and $\lambda_{j,2}$ ($i=1, \ldots, N_1$ and $j=1, \ldots, N_2$). The reproductive potential is determined by several factors, including the parent's age, weight, residence time on the spawning ground. It should be noted that the magnitude of this parameter includes information about the survival rate of the offspring, the number of days after egg hatching, and the egg number; this implies that the parameter reflects the sample timing. It should also be noted that the modeling framework does not depend on whether the reproductive potential is heritable or not.

@@

In the process of the derivation of $\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$ in {\bf APPENDIX 2}, we ignore covariation between migration and reproductive potential. Here, we consider the situation in which migrants have a distinguishable distribution of reproductive potential from non-migrant parents. Let $\lambda_{i,1}$, $\lambda_{j,2}$, $\lambda_{M,l,1}$ and $\lambda_{M,l,2}$ be a reproductive potential of non-migrant in the population 1 and 2 and migrants in the population 1 and 2 with mean ${\bar \lambda_{1}}$, ${\bar \lambda_{2}}$, ${\bar \lambda_{M,1}}$ and ${\bar \lambda_{M,2}}$, respectively. Under this setting, $\pi_{\rm HS,bet}$ can be written by
\begin{align}
\pi_{\rm HS,bet} &\approx \frac{4}{M}  \frac{ \mathbb{E}\left[ \sum_{l=1}^M \lambda_{M,l,1} \sum_{l=1}^M \lambda_{M,l,2} \right]} {\mathbb{E}\left[ \left(\sum_{l=1}^{M} \lambda_{M,l,1} + \sum_{i=M+1}^{N_1} \lambda_{i,1}\right) \left(\sum_{l=1}^{M} \lambda_{M,l,2} + \sum_{j=M+1}^{N_2} \lambda_{j,2}\right) \right] }\nonumber\\ 
&= \frac{4}{M} \frac{ M^2 {\bar \lambda_{M,1}} {\bar \lambda_{M,2}} } { \left( M {\bar \lambda_{M,1}} + (N_1 - M) {\bar \lambda_1} \right) + \left( M {\bar \lambda_{M,2}} + (N_2 - M) {\bar \lambda_2} \right)}.
\label{App3}
\end{align}
If ${\bar \lambda_{M,1}} = {\bar \lambda_{1}}$ and ${\bar \lambda_{M,2}} = {\bar \lambda_{2}}$, Eq.~\ref{App3} reduces to Eq.\ref{App2}. This formulation include reproductive potential terms, so that distinct reproductive potential between migrants and non-migrants vanishes the usefulness from proposed HS-based estimators (this is also applied to PO-based estimators proposed in this paper).
